Analyzing Buildlogs Using Programming by Example

### 2019-05-03 paper/paper.tex
outline, introduction notes

>>>>

\section{Introduction}
ci important for sw projects, broken build stops dev process until its fixed, shortening fixing time important to increase dev productivity, to detect underlying failure huge buildlog has to be read, finding relevant information between a lot of lines unimportant for that task, extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity, few existing approaches on specifically that domain, ... our approach ...

\section{Related Work}
\paragraph{CI Research}
google paper, ing \& os java paper, travistorrent
\paragraph{Analyzing Buildlogs}
maven/java paper
\paragraph{Information Extraction}
prose flashextract

TODO put in proper references to the papers youre surely gonna need here

\section{Background}
program synthesis from example, neccessary theoretical stuff

here all the references to prose theoretical papers

\section{Data collection}
describe process of collecting buildlog files, sampling

\section{Meta-Model}
describe metamodel of data obtainable from buildlogs

\section{Our Tool}

\section{Evaluation}

\section{Conclusion and Future Work}
